\section{Conclusions and Future Work}
To sum up, we apply formal methods to guarantee the absence of any misbehavior during the development process of buddy allocation model, the specification level in this paper. Our specification starts directly at the algorithm level, where our work is different from others'. By the proofs of satisfaction in preconditions and postconditions as well as invariants, we ensure the specification a functionally correct one. After that, we introduce the integrity property for the security assurance of buddy allocation model. To achieve this, we design a state-machine driven security model, which satisfies integrity property. By introducing interfaces to the buddy memory model as an event specification, we finally proved that the event specification based on our memory model satisfies the integrity property.

Our memory model specification is currently abstract on address spaces, which are replaced by the concept of \emph{ID} in a leaf. The mapping between a \emph{ID} and a true range of address and the one-to-one uniqueness guarantee are arranged to the next more specific specification level. Another next step is to show our memory model specification by introducing the semantics of a language like \emph{Simpl}. By refinement between the specification level and semantics language level, and automatic transition into implementation level, we try to offer C codes for our buddy allocation algorithms. Ultimately, we aim to offer reliable buddy memory codes to any operation systems that apply this kind of algorithms.
