
\section{Introduction}
Correctness of applications and libraries of a system using dynamic memory allocation rely on properties the memory have to preserve. Errors in any stage of the development process of the memory management component, may break those properties, leading to critical issues in the rest of the system. Along the last decades, formal methods have been successfully applied in the verification of critical systems. To improve confidence on the reliability of a memory management, verification of functional correctness and security properties is applied from the top specification layers down to the implementation and the machine code. 

Formal verification has been applied on memory managers going from very abstract models to more concrete ones. For instance, the work in~\cite{reg_higham} formalizes an abstraction of the memory management in term of write and read operations. They prove sequential consistency over the abstraction, so the memory is expressed as ordered sequence of reads and writes. Also focussing on a high level of abstraction, the work in~\cite{reg_blazy} provides a memory model for an imperative language, defining the necessary memory operations for the language at the specification and implementation levels. It defines an axiomatic reasoning framework, proving that the memory semantics satisfy such axiomatic rules. In a similar way~\cite{reg_mansky}, also provides an axiomatic proof system for a sequential memory model, bringing together a unified representation of the memory rules. In this sense, the work in~\cite{reg_mansky} proves that their memory rules also satisfy the ones in~\cite{reg_blazy}.


The work from~\cite{reg_peter} formally specify a buddy allocation algorithm verifying the absence of covert channels on it.


In this paper, we develop a specification for buddy allocation algorithms in the Isabelle/HOL proof assistant. The budy allocation algorithms provide to applications with two services for the allocation and disposal of memory blocks. Our specification must consists of algorithm details as specific as possible for the sake of capturing any feature in the algorithms. Then we specify and prove a number of properties for functional correctness of the algorithm. Finally, we show that the memory services preserve integrity of other memory areas previously allocated.

The following section briefly introduces the Isabelle/HOL verification environment. The next section is about the formalization of buddy allocation model including representation of our specification and proofs to properties for functional correctness. The verification of integrity for security is arranged in the following section. The last section is about the conclusions and future work.


